Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-22 latex/article.tex
sect4

@@

>>>>

 Compared to the hierarchical approach, no precomputation is required
 for a given radius $R$. As a consequence, we could even locally adapt
 the ball radius to the geometry (for instance following the octree
 depth of the current MC vertex). In the next section, we evaluate the
 performances of both approaches.

@@

\subsection{Full resolution experiment}

\subsection{Fully adaptive evaluation}
